When easy is not preferred: A discounting paradigm to assess load-independent task preference

### 2023-02-24 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
corrected sentence

Regardless of the preprocessing pipeline, *n*-back level and *d'* were significant predictors of SVs, and had stable effect estimates across all pipelines.
The only pipelines, in which the median RT was a significant predictor of SVs, were the three pipelines with the highest Bayes Factors and the largest effect of *n*-back level.
These three pipelines contain data that has been inverse transformed across subjects but within conditions, i.e. within the round of an *n*-back level.
The two "spikes" in the beta of the median RT in Figure\ \@ref(fig:sca-plot) are from the other two pipelines that used inverse transformation.

@@

>>>>

Regardless of the preprocessing pipeline, *n*-back level and *d'* were significant predictors of SVs, and had stable effect estimates across all pipelines.
The only pipelines, in which the median RT was a significant predictor of SVs, were the three pipelines with the highest Bayes Factors and the largest effect of *n*-back level.
These three pipelines contain data that has been inverse transformed across subjects but within conditions, i.e. within the round of an *n*-back level.
The by far highest values of the beta of the median RT in Figure\ \@ref(fig:sca-plot) are all from the pipelines that used inverse transformation.

@@

We used an rmANOVA to investigate whether the difference between the SVs of 1- and 2-back, and 2- and 3-back, respectively, depended on whether a participant's NFC score was above or below the median.
There was a main effect of the *n*-back level (`r apa_print(hypothesis3a_model)$full_result$nlevels`), but neither a main effect of the NFC group (`r apa_print(hypothesis3a_model)$full_result$nfcmedian`) nor an interaction of NFC group and *n*-back level (`r apa_print(hypothesis3a_model)$full_result$nfcmedian_nlevels`).
Post-hoc tests showed that the difference between the SVs of 2- and 3-back is slightly more negative than the difference between 1- and 2-back (`r apa_print(pairs(hypothesis3a_emm_nlevel))$full_result`), but there are large interindividual differences, especially for 2- and 3-back (Figure\ \@ref(fig:h3a-plot)).
This means that across the whole sample, there was a steeper decline in SVs from 2- to 3-back than from 1- to 2-back, but some participants showed a completely opposite pattern.

INSERT FIGURE 3 HERE

```{r h3a-plot, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Difference scores in the subjective values of 1- minus 2-back and of 2- minus 3-back.", fig.pos="H"}

  print(plot_h3a)
